30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
Added correct citing for MorphMix and changed some sentence structure.

		\subsection{MorphMix}
			MorphMix functions similar to both Tor and MIX networks. It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication. Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.

@@

			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism. Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel. A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel. To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel. Although this makes the possibility of such an attack more difficult, it is not impossible.

>>>>

		\subsection{MorphMix}
			MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks. It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication. Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.

@@

			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism. Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel. A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel. To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel. Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
